A Survey on Ordered Binary Decision Diagrams

### 2015-09-10 figs/obdd.tex
Fix line width

    \draw[dashed] (A.south west) -- (Bl.north east);
    \draw (A.south east) -- (Br.north west);

    \draw[dashed] (Bl.south east) -- (C.north west);
    \draw (Bl.south) -- (0.north);

    \draw[dashed] (Br.south west) -- (C.north east);
    \draw (Br.south) -- (1.north);

    \draw[dashed] (C.south west) -- (0.north);
    \draw (C.south east) -- (1.north);
\end{tikzpicture}

>>>>

    \draw[thick, dashed] (A.south west) -- (Bl.north east);
    \draw[thick] (A.south east) -- (Br.north west);

    \draw[thick, dashed] (Bl.south east) -- (C.north west);
    \draw[thick] (Bl.south) -- (0.north);

    \draw[thick, dashed] (Br.south west) -- (C.north east);
    \draw[thick] (Br.south) -- (1.north);

    \draw[thick, dashed] (C.south west) -- (0.north);
    \draw[thick] (C.south east) -- (1.north);
\end{tikzpicture}
